---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}

```

## What's the Deal with YouTube Sponsors?

```{r}
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTAI3f0c1YqJ1fks5WrrpgwsJ6cR4fU4FqEI6uXsr5hdhTRWUOzgAgd3q3lD7Aua9P9LrXjnZIUIGE1/pub?output=csv")

latest_data <- logged_data %>%
  rename(video_category = 2,
         video_length = 3,
         subscriber_count = 4,
         upload_date = 5,
         sponsor_name = 6)

latest_data <- latest_data %>%
  mutate(video_length = as.numeric(hms(video_length)))


total_no <- length(latest_data$Timestamp)

max_length <- max(latest_data$video_length)

min_length <- min(latest_data$video_length)

sponsor_count <- latest_data %>%
  count(sponsor_name, sort = TRUE)

category_count <- latest_data %>%
  count(video_category, sort = TRUE)

```

Sponsors, how do they work?
We'll be counting up sponsor appearances in YouTube videos and comparing them to the category of said video to see if we can find any patterns. 

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = video_category, 
               fill = sponsor_name)) +
  labs(title = "Sponsorship Density by Video Category",
       x = "Video Category",
       y = "Sponsor Count",
       fill = "Sponsor Name") +
  scale_x_discrete(guide = guide_axis(angle = 90))
```

Out of `r total_no` sponsored videos between `r min_length` and `r max_length` seconds long, the most common sponsor is *`r sponsor_count$sponsor_name[1]`*.

<br>
<br>
<br>

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = sponsor_name, 
               fill = video_category)) +
  labs(title = "Video Category by Sponsorship Density",
       x = "Sponsor Name",
       y = "Video Count",
       fill = "Video Category") +
  scale_x_discrete(guide = guide_axis(angle = 90))

```

In terms of videos with sponsors, videos in the *`r category_count$video_category[1]`* category tended to have a larger number of sponsors compared to the others.
